Type Evolution in Programming Systems

### 2024-05-29 paper.tex
fix planetscale bib

Such situations are common in software engineering. Web backend architectures often put data and
code on separate machines, which makes it impossible to update both atomically. To perform
upgrades, teams must manually perform multi-step zero-downtime deployment processes~\cite{planetscale}
to step the database and the code servers forward gradually such that they are compatible with one
another at any given step. One example would be deploying a change to add a database column
before deploying the code that uses the column.

>>>>

Such situations are common in software engineering. Web backend architectures often put data and
code on separate machines, which makes it impossible to update both atomically. To perform
upgrades, teams must manually perform multi-step zero-downtime deployment processes~\cite{planetscalerails}
to step the database and the code servers forward gradually such that they are compatible with one
another at any given step. One example would be deploying a change to add a database column
before deploying the code that uses the column.
